\section{Work Distribution}

The project work was divided primarily by assignment stage. Teodor was mainly responsible for assignments 2, 4, and 5, and shared assignment 6. I was mainly responsible for assignments 1 and 3, and also shared assignment 6. If only the implementation assignments are considered, this gives an approximate 60/40 split in Teodor's favour.

The report writing was distributed somewhat differently. I wrote approximately 60\% of the report text, which balanced much of the earlier implementation difference. Taken together, the implementation work and the report writing therefore gave a contribution split that was close to 50/50 overall, which we consider a reasonable balance for a group project of this type.

We also worked deliberately to maximize learning from the parts of the project that each of us had not implemented directly. After each work session, we wrote short notes describing what had been done, what design choices had been made, and what problems had appeared. This made it possible for the other person to read the notes afterward and then write that part into the report with a clear understanding of both the implementation and the reasoning behind it.

In practice, this meant that when Teodor implemented an assignment task, I would usually write the corresponding report section, and the same principle also applied in the opposite direction. This gave both of us a reason to study and explain the other person's work instead of only documenting our own. In that way, the report became part of the learning process rather than a duplicate writing pass over the same task.
